Enrich the datasets with new columns.

### 2020-08-20 inst/analysis/analysis_stable.Rmd

```{r group_expr_functions}
group_expr_functions <- expr_call_arg %>%
                            mutate(function_expr2 = if_else(str_starts(expr_expression_function, fixed("(function(")), "anonymous", expr_expression_function))

@@

```{r arity_expr_expression_plot}
expr_call_arg %>% ggplot() + 
  geom_bar(aes(x = fct_rev(fct_infreq(expr_expression_args_num)))) +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n")

@@

```{r arity_expr_expression_plot_per_eval}
expr_call_arg %>% ggplot() + 
  geom_bar(aes(x = fct_rev(fct_infreq(expr_expression_args_num)))) +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n") +
  facet_wrap(vars(eval_function))
```

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            mutate(function_expr2 = if_else(str_starts(expr_resolved_function, fixed("(function(")), "anonymous", expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "="),
                              read = c("[", "[[", "$"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo"),
                              expressions = c("as.list", "expression", "as.name", "as.expression", "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              classAssign = c("@<-"),
                              classRead = c("slot", "@"),
                              classDef = c(".Primitive(\"class\")"),
                              logical = c("<", ">", "is.element"),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

```{r arity_expr_resolved_plot}
expr_resolved_call_arg %>% ggplot() + 
  geom_bar(aes(x = fct_rev(fct_infreq(expr_resolved_args_num)))) +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n")

@@

```{r arity_expr_resolved_plot_per_eval}
expr_resolved_call_arg %>% ggplot() + 
  geom_bar(aes(x = fct_rev(fct_infreq(expr_resolved_args_num)))) +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n") +
  facet_wrap(vars(eval_function))
```

>>>>

```{r group_expr_functions}
group_expr_functions <- expr_call_arg %>%
                            #mutate(function_expr2 = if_else(str_starts(expr_expression_function, fixed("(function(")), "anonymous", expr_expression_function))
                            mutate(function_expr2 = groupify_function(expr_expression_function)) %>%

@@

```{r arity_expr_expression_plot}
expr_call_arg %>% ggplot() + 
  geom_bar(aes(x = expr_expression_args_num)) +
  scale_y_sqrt() +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n")

@@

```{r arity_expr_expression_plot_per_eval}
expr_call_arg %>% ggplot() + 
  geom_bar(aes(x = expr_expression_args_num)) +
  scale_y_sqrt() +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n") +
  facet_wrap(vars(eval_function))
```

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            #mutate(function_expr2 = if_else(str_starts(expr_resolved_function, fixed("(function(")), "anonymous", expr_resolved_function)) %>%
                            mutate(function_expr2 = groupify_function(expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "="),
                              read = c("[", "[[", "$"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo"),
                              expressions = c("as.list", "expression", "as.name", "as.expression", "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              classAssign = c("@<-"),
                              classRead = c("slot", "@"),
                              classDef = c(".Primitive(\"class\")"),
                              logical = c("<", ">", "is.element"),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              primitive = c("primitive"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

```{r arity_expr_resolved_plot}
expr_resolved_call_arg %>% ggplot() + 
  geom_bar(aes(x = expr_resolved_args_num)) +
  scale_y_sqrt() +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n")

@@

```{r arity_expr_resolved_plot_per_eval}
expr_resolved_call_arg %>% ggplot() + 
  geom_bar(aes(x = expr_resolved_args_num)) + 
  scale_y_sqrt() +
  coord_flip() + 
  labs(title = "Arity of calls", x = "arity", y = "n") +
  facet_wrap(vars(eval_function))
```

### 2020-08-20 inst/analysis/enrich_dataset.Rmd

Let's remove the duplicate ones (but keep:

@@

```{r}
eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "enriched_calls.fst"))

>>>>

Let's remove the duplicate ones (but keep their numbers):

@@

```{r}
#eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "deduplicated_calls.fst"))
